---
title: "How to Use MboxR"
author: "JooYoung Seo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Use MboxR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# mboxr

The goal of mboxr is to allow R users to conveniently import an [**mbox file**](https://en.wikipedia.org/wiki/Mbox) into [**R tibble**](https://tibble.tidyverse.org/) for hands-on analyses in R environment.

# Installation

## Python Dependencies

`mboxr` requires Anaconda Python environment on your system Path.

If you have not installed Conda environment on your system, please [download and install Anaconda](https://www.anaconda.com/download/) (Python 3.6 or later is recommended).

For this package, I have implemented [**mailbox.mbox**](https://docs.python.org/3/library/mailbox.html), [**pandas.DataFrame**](https://pandas.pydata.org/), and [**email.header.decode_header**](https://docs.python.org/3/library/email.header.html) Python modules into R using [**reticulate**](https://rstudio.github.io/reticulate/).

## R Package Installation

### Development Version

You can install the latest development version as follows:

```{r, eval=FALSE}
if(!require(devtools)) {
install.packages("devtools")
}

devtools::install_github("jooyoungseo/mboxr")
```

### Stable Version

You can install the released version of mboxr from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
install.packages('mboxr')
```

## Usage

Please use `read_mbox()` function after loading `mboxr` library like below:

```{r test, eval=F}
library(mboxr)
# Importing your mbox file into an R:
test <- system.file("extdata", "test1.mbox", package = "mboxr")
data <- read_mbox(test)
str(data)
#> Classes 'tbl_df', 'tbl' and 'data.frame':    2 obs. of  5 variables:
#>  $ date   : chr  "Fri Jul  8 12:08:34 2011" "Fri Jul  8 12:08:34 2011"
#>  $ from   : chr  "author@example.com" "author@example.com"
#>  $ to     : chr  "recipient@example.com" "recipient@example.com"
#>  $ subject: chr  "Sample message 1" "Sample message 2"
#>  $ content: chr  "This is the body.\n>From (should be escaped).\nThere are 3 lines.\n" "This is the second body.\n"

# Or, you can save your mbox file as a CSV file while assigning a tibble variable at the same time like below:
data <- read_mbox(test, "output.csv")
data
#> # A tibble: 2 x 5
#>   date         from       to         subject    content                    
#>   <chr>        <chr>      <chr>      <chr>      <chr>                      
#> 1 Fri Jul  8 ~ author@ex~ recipient~ Sample me~ "This is the body.\n>From ~
#> 2 Fri Jul  8 ~ author@ex~ recipient~ Sample me~ "This is the second body.\~

# You can merge all mbox files in your current directory or in any specified path into one tibble and save csv file for the integrated one:
test_path <- system.file("extdata", package = "mboxr")
all_data <- merge_mbox_all(path = test_path, out = "all_merged_mbox.csv")
## Find your "output.csv" file saved in your computer while freely using the imported tibble in your R session!
all_data
#> # A tibble: 4 x 5
#>   date         from      to         subject      content                   
#>   <chr>        <chr>     <chr>      <chr>        <chr>                     
#> 1 Fri Jul  8 ~ author@e~ recipient~ Sample mess~ "This is the body.\n>From~
#> 2 Fri Jul  8 ~ author@e~ recipient~ Sample mess~ "This is the second body.~
#> 3 Sat Jul  9 ~ author@e~ recipient~ Another sam~ "R is the best!\nLet's us~
#> 4 Sun Jul  10~ author@e~ recipient~ The last sa~ "This is the last message
```

