---
title: "How to Use MboxR"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Use MboxR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# mboxr

The goal of mboxr is to allow R users to conveniently import an mbox file into R data_frame for hands-on analyses in R environment.

# Installation

## Python Dependencies

`mboxr` requires Python 3.x on your system Path.

Please check whether Python 3.x is available on your system first, if not, install Python version 3.x beforehand.

## R Package Installation

`mboxr` has not been submitted to CRAN. Please install the package using `devtools` like below:

```{r, eval=F}
if(!require(devtools)) {
install.packages("devtools")
}

devtools::install_github("jooyoungseo/mboxr")
```

## Usage

Please use `read_mbox()` function after loading `mboxr` library like below:

```{r, eval=F}
library(mboxr)
# Importing your mbox file into an R:
data <- read_mbox("your_file.mbox")

# Or, you can save your mbox file as a CSV file while assigning a data_frame variable at the same time like below :
data <- read_mbox("your_file.mbox", "output.csv")
## Find your "output.csv" file saved in your computer while freely using the imported data_frame in your R session!
```
